Hydras \& Co.

### 2022-04-13 doc/gaia-chapter.tex
add a new subsection

>>>>

\subsection{Back to hydras}

In \href{../theories/html/gaia_hydras.GHydra.html}%
{\texttt{gaia\_hydras.GHydra}}, we import a few theorem abouthydra battles (see
~\href{../theories/html/theories/html/hydras.Hydra.Hydra_Theorems.html}{Hydra.Hydra\_Theorems}).

\subsubsection{Termination of all battles}

The termination measure is re-defined with \gaia's ordinals.

\inputsnippets{GHydra/mDef}.

\inputsnippets{GHydra/mVariant, GHydra/Termination}.

\subsubsection{Length of standard battles}

Finally, we relate the lenght of standard-battles with the $L_\alpha$ fast growing functions.

\inputsnippets{GHydra/lDef, GHydra/lStdOk}.
